Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-06-24 paper.tex
Finished for resubmission

			\noindent Typicality is one of the key concepts that will be used in this paper, so it is fundamental that it is defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, as defined in this paper, a measure of how representative 
			an example is of their category and of the other members of the same category.

@@

			\noindent Prototypes are another key concept used in this paper and, as the concept of typicality, should be defined. In this case, there are some differences based on the field that it is 
			examined. According to Murphy's Big Book of Concepts\cite{Murphy:2002}, a prototype is the best example of a category, which corresponds to the most typical item. In this case 
			it is specified that this item may not be something that exists physically, but it is an average of what people see from real world examples. Adopting the example that the 
			author uses in the book, which is about dogs, ``just your abstraction of what dogs are most often like''. This opens the possibility to the fact that every person has, for the 
			same category, a different prototype. That is why, in this paper, the prototypes will be treated as an average, among different people, of the examples weighted with the 
			average perceived typicality.\\
			Although this is the concept of prototype that will be used in this paper, there are numerous different possibilities. For example, could be intended in a software-engineering way 
			as the first example of a new product, or in a HCI-like way as a representation of conceptual design as stated by Prof. Narges Mahyar of the University of 
			Massachusetts \cite{hciprot}. Another example is the concept of prototype used by Smith et al. in an article, in which they stated that a prototype is ``a prestored representation 
			of the usual properties associated with the concept's instances'' \cite{smith1988combining}. This view in some way generalizes the definition expressed by Murphy in his book. \\
			For the goal of this paper, the best way to define a prototype is the one used by Murphy, although with a small modification to take into account also the typicality of every 
			example to create the prototype. Also Smith's way to define a prototype would be interesting to use, but since Murphy's way is a bit more specific, it is probably easier to use.

@@

					One of the first feature extraction methods implemented in image processing is edge detection.				
					In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
					These are usually divided into two groups, gradient-based and Gaussian-based. 
					Some examples are the Sobel operator and the Canny edge detector. 
					Each algorithm has its own peculiarities and it is the user's job to find 
					the most appropriate for its goal~\cite{owotogbe2019edge}.\\

@@

@@

					A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{felzenszwalb2005representation}. For the goal of the experiment proposed here, some deformable shape 
					detection techniques can be useful. \\
					The technique proposed strongly relies on the triangulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
					The author also make use of the properties of chordal graphs and k-trees.\\
					The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
					possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since, depending on the formulation of the energy function, the costs 
					can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually require an initialization near to the correct solution, 
					although this is not required for the algorithm presented in this paper. For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor.

@@

					After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
					\noindent In 2019, a paper written by Varshni et al. that proposes a method~\cite{varshni2019pneumonia} to classify images using CNNs, trying to understand if a patient 
					has pneumonia or not. After the preprocessing, there is the feature extraction process. For this step, the authors used different pretrained models.
					In this paper's results it is reported that the best model architecture is DenseNet-169.

					\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumours~\cite{gumaei2019hybrid}. The process described in the paper is divided into three points. The 
					first one is preprocessing, the second is feature extraction and the third is brain tumour classification. The first step is just to rescale the values to the range $[0,1]$. The feature extractor 
					used is the GIST descriptor. The GIST is then combined with a Gabor filter and produces a total of $mxnx4x4$ GIST feature vectors. There is a variant of the GIST descriptor, the 
					PCA-NGIST is a PCA-based normalized GIST feature extraction method. The NGIST is a normalized version of the GIST descriptor, that uses the L2 norm to make the GIST invariant to illumination and shadowing. 
					After this step, the only thing left is the classification of the tumour, which was performed with a RELM classifier.

@@

					Although there exists techniques that can extract features from hyperspectral images, this kind of images are created to capture the entire spectrum. This fact means that these images can capture 
					more information then what the human eye can. The techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent 
					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it is probably more meaningful to use normal 
					images than these ones.

@@

					Convolutional neural networks are not an extremely recent type of neural network, especially if we consider that LeNet-5 was created in 1998. Scientists have dealt with CNNs for some years. Now, as of 2022, 
					CNNs are mostly used to deal with images.\\
					In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs~\cite{wu2017introduction}. These networks use mostly three kind of layers: Dense layers (which are fully connected layers), 
					Convolutional layers and Pooling layers. In the following, there will be a short description of each kind of layer. 
					\begin{itemize}

@@

					Siamese neural networks, also called twin networks, are a more recent advance in computer science. These neural networks have a different structure from convolutional neural networks. The 
					structure of siamese neural networks is peculiar. In fact, there are two identical networks, called embedding networks, that process different inputs and, after that, 
					they merge in a single layer that measures the similarity between 
					the two outputs of the two networks. The siamese neural networks have a different application compared to CNNs, in fact twin networks are mainly used to measure similarity of two objects. 
					In the case of this paper, the siamese neural networks are used for image matching. This is not the first time that siamese networks are used for image matching, as shown in a paper written in 2016 by 
					Melekhov et al.~\cite{melekhov2016siamese}, but with a little difference in the objective of the matching. The objective of the paper was to learn a general similarity for image retrieval, while on the case of this 
					paper, the objective is to find a similarity measure with a prototype.

@@

				\noindent In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017~\cite{appalaraju2017image}. In this work they explore the possibility to 
				find a similarity measure for image retrieval. To achieve this goal, they implemented a siamese neural network that uses two identical multi-scale CNNs that share weights. The ouput of the 
				network is binary, being $1$ the label to predict in case of negative examples and $0$ the label to predict in case of positive example. The loss function used in this work is a contrastive loss. This paper 
				then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspired by curriculum learning, that helps reducing the training time. \\
				This is not the only work that uses neural networks to learn similarity, in fact there are also other application fields for similarity study. One of them is healthcare, as shown in a paper by Suo et al., written in 
				2017, that introduces a model used to make personalized prediction of diseases for patients, basing the prediction on a similarity related method, learned using CNNs~\cite{8217759}. In this paper, before 
				learning the actual similarity measure, the authors processed the input through a CNN and performed a step they call ``Time fusion''. This step let them incorporate the time information and 
				weight differently eventual symptoms based on their temporal distance from the first appearance of the disease. Only after this step the authors proceeded to learn a similarity metric, basing the learning 
				on CNNs.\\
				Another paper, written by Chopra et al. in 2005, used a method similar to the one written by Appalaraju. In this work, the authors used a siamese architecture to learn a similarity metric and applied it 
				in the field of face verification~\cite{chopra2005learning}.\\
				More interestingly, there are also other papers, in particular a paper by Attarian et al. written in 2020 uses $VGG16$. This paper's goal is to use this CNN to predict human similarity 
				judgments~\cite{attarian2020transforming}. Using $VGG16$, the authors were able to achieve good results, with over 90\% in validation accuracy.

@@

			\noindent Another possibility for collecting typicality values is the typicality ranking. With this method the researcher asks subjects to rank a set of objects based on their typicality. After doing so 
			and collecting the data, the researcher should infer the typicality values based on the ranking. The ranking, as the rating described in \ref{sec:typval}, cannot be performed on all images of the dataset, 
			so it's necessary to split the ranking and rank the images in different forms and then use the informations coming from different subjects and infer the informations about typicality from these answers.

@@

		\subsection{Considerations about the survey\lable{sec:cas}}

			\subsubsection{Considerations}
				\noindent The first two presented methods have a quite similar concept behind them. Although it is still a matter of discussion which one is more reliable, especially in children, as seen in \cite{maridaki1997rating} 
				and \cite{10.1371/journal.pone.0157936}, both these methods have been used to collect typicality informations. The main difference in these two methods is that the first one, which is based on 
				ratings, the researchers may have biased data since it is possible that seeing a picture of an example of the category the subject can be biased. On the other hand, the other method does not present 
				this kind of bias, but presents a higher difficulty on in extracting the typicality values. \\
				The alternative possible proposed method, can show a lower bias than the bias of the rating method since no images influence the subject's ratings. Moreover, it is easier to infer a typicality value 
				than in the ranking method, since a higher position on the list corresponds to a higher typicality. 
				Another positive aspect of this method is that if a person did not think of a particular example, it won't appear on the ratings. This fact can help identifying the real typicality 
				without the possible bias introduced by presenting to a subject an image of an example that did not come to mind.

@@

				\noindent The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole 
				dataset, since it must have many images. In fact, it is very likely that a subject that has to rate or rank many examples will be tired after a certain number of images, polluting the results of the survey.
				The possible solution to this problem, is to give the subjects a subset of images to rate or rank. In this way, the collected data are most likely more reliable than the ones collected on all the dataset, 
				so it is more accurate the final result. \\
				Regarding only the typicality rating system, there is another problem. As hinted in previously, there is the possibility that this procedure leads to biased data. That is true because the form 
				created to collect the data, presents an example of an object that the subjects may not have thought of, and presenting the image, it may be possible that the subject gives a biased answer since 
				the image could have influenced the subject's judgement. For example, let us assume that the category chosen for the experiments is ``bird''. If a person is presented and image of a swan, 
				or a duck, and is asked to rate its typicality, most likely will rate it in the higher part of the scale, while if asked to list a certain number of birds it is more likely that it is not 
				present than that it is present.\\
				Talking about the ranking system, also this method can present biased data, since also this method presents the images, even if the bias is probably lower than the one that could result with the ranking system. 
				The major problem, with this method, is that the researcher must also design an algorithm to infer the typicality values from the rankings. This is a very difficult algorithm to design, since the rankings must 
				find a mapping to a scale.\\
				The alternative possibility described, can result in a lower bias since no images influence the subject's judgments. Recalling the previous example, in fact, if the subject did not think of 
				ducks and swans in the category ``bird'', these examples will not appear on the list. Although this technique presents a lower bias, it results in a great difficulty in prototype construction.

			\subsubsection{Considerations on how to choose}

@@

		\subsection{Considerations about prototype construction\label{sec:cpc}}

			\noindent The prototype depends on the feature extraction technique that was used. As discussed in Section \ref{sec:fe}, the key difference is human interpretability. In fact, building a prototype using the 
			classical feature extraction methods, results in an image that can be seen and interpreted. Using a prototype generated with machine learning feature extraction techniques results in an array 
			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
			a work by Carvalho written in 2019~\cite{electronics8080832}, 
			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the European Union in the field of artificial intelligence. In particular, there is a document of 
			the act\footnote{\url{https://eur-lex.europa.eu/resource.html?uri=cellar:e0649735-a372-11eb-9585-01aa75ed71a1.0001.02/DOC_1&format=PDF}} that states that there will be some requirements in terms of 
			transparency and interpretability for machine learning systems that are considered high-risk AI. The growing interest produced some results, but still they are not enough to easily interpret machine learning 
			features.\\
			Most likely, in the future will be possible to look at the features extracted by a neural network and comprehend their meaning. When this will be possible, independently of the feature extraction techniques 
			used, the human interpretability will be possible, and with that in mind it would be probably more convenient to extract the features using neural networks. The reason behind this consideration is 
			that although the training of a neural network can be expensive in computational terms, the evaluation of an input on a trained network it is not very computationally demanding. On the other side, algorithms 
			like the triangulation always have the same demand, that is lower than the demand of training a neural network, but surely higher than the demand of evaluating a single input on a convolutional neural network. 
			Moreover, considering the possibility to use transfer learning techniques, the training can become a fine-tuning or a domain adaptation problem, which means the computational load is lighter. Considering that 
			the fact that the training is a demanding task to be performed only once and that other algorithms may be less demanding but must be run multiple times, it is probably more convenient to train a neural 
			network. Moreover, not only the feature extraction process is convenient, but also the prototype construction itself is more convenient if the features are in the form of numerical parameters, since it is 
			enough to perform a weighted average, a simpler operation if confronted with the construction of a new image that should take into account features of numerous other images.
			Moreover, scientists will be presented a tough challenge, since the construction of an image using the average of other images is not an easy task. In this task there are in particular two problems. The first 
			one is that there is no clear algorithm to average two different images as it is requested in this paper, 
			and it is even more difficult to compute a weighted average. In fact, the in Figure \ref{fig:8}, it is difficult to even imagine what the result of this weighted average should be.

			\begin{figure*}[!t]
				\centering
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
				\end{subfigure}
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.4\linewidth]{imgs/swallow_2_edges.jpg}}
				\end{subfigure}
				\caption{Edge extraction of different swifts}
				\label{fig:9}
			\end{figure*}

>>>>

			\noindent Typicality is one of the key concepts that will be used in this paper, so it is fundamental that it is defined. In a paper by Dieciuc and Folstein \cite{dieciuc2019typicality},
			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, as defined in this paper, a measure of how representative 
			an example is of their category and of the other members of the same category.

@@

			\noindent Prototypes are another key concept used in this paper and, as the concept of typicality, should be defined. In this case, there are some differences based on the field that it is 
			examined. According to Murphy's Big Book of Concepts \cite{Murphy:2002}, a prototype is the best example of a category, which corresponds to the most typical item. In this case 
			it is specified that this item may not be something that exists physically, but it is an average of what people see from real world examples. Adopting the example that the 
			author uses in the book, which is about dogs, ``just your abstraction of what dogs are most often like''. This opens the possibility to the fact that every person has, for the 
			same category, a different prototype. That is why, in this paper, the prototypes will be treated as an average, among different people, of the examples weighted with the 
			average perceived typicality.\\
			Although this is the concept of prototype that will be used in this paper, there are numerous different possibilities. For example, could be intended in a software-engineering way 
			as the first example of a new product, or in a HCI-like way as a representation of conceptual design as stated by Prof. Narges Mahyar of the University of 
			Massachusetts \cite{hciprot}. Another example is the concept of prototype used by Smith et al. in an article, in which they stated that a prototype is ``a prestored representation 
			of the usual properties associated with the concept's instances'' \cite{smith1988combining}. This view in some way generalizes the definition expressed by Murphy in his book. \\
			For the goal of this paper, the best way to define a prototype is the one used by Murphy, although with a small modification to take into account also the typicality of every 
			example to create the prototype. Also Smith's way to define a prototype would be interesting to use, but since Murphy's way is a bit more specific, it is probably easier to use.

@@

@@

					One of the first feature extraction methods implemented in image processing is edge detection.				
					In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
					These are usually divided into two groups, gradient-based and Gaussian-based. 
					Some examples are the Sobel operator and the Canny edge detector. 
					Each algorithm has its own peculiarities and it is the user's job to find 
					the most appropriate for its goal \cite{owotogbe2019edge}.
					An example of the result of this process is in Figure \ref{fig:1}.\\

@@

					A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes \cite{felzenszwalb2005representation}. For the goal of the experiment proposed here, some deformable shape 
					detection techniques can be useful. \\
					The technique proposed strongly relies on the triangulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
					The author also make use of the properties of chordal graphs and k-trees.\\
					The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
					possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since, depending on the formulation of the energy function, the costs 
					can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually require an initialization near to the correct solution, 
					although this is not required for the algorithm presented in this paper. For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor.

@@

					After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
					\noindent In 2019, a paper written by Varshni et al. that proposes a method \cite{varshni2019pneumonia} to classify images using CNNs, trying to understand if a patient 
					has pneumonia or not. After the preprocessing, there is the feature extraction process. For this step, the authors used different pretrained models.
					In this paper's results it is reported that the best model architecture is DenseNet-169.

					\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumours \cite{gumaei2019hybrid}. The process described in the paper is divided into three points. The 
					first one is preprocessing, the second is feature extraction and the third is brain tumour classification. The first step is just to rescale the values to the range $[0,1]$. The feature extractor 
					used is the GIST descriptor. The GIST is then combined with a Gabor filter and produces a total of $mxnx4x4$ GIST feature vectors. There is a variant of the GIST descriptor, the 
					PCA-NGIST is a PCA-based normalized GIST feature extraction method. The NGIST is a normalized version of the GIST descriptor, that uses the L2 norm to make the GIST invariant to illumination and shadowing. 
					After this step, the only thing left is the classification of the tumour, which was performed with a RELM classifier.

@@

					Although there exists techniques that can extract features from hyperspectral images, this kind of images are created to capture the entire spectrum. This fact means that these images can capture 
					more information then what the human eye can. The techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent 
					networks, as seen in a paper by Hu et al. \cite{hu2020spatial} and in a paper by Rasti et al. \cite{rasti2020feature}. For the reasons just said, it is probably more meaningful to use normal 
					images than these ones.

@@

					Convolutional neural networks are not an extremely recent type of neural network, especially if we consider that LeNet-5 was created in 1998. Scientists have dealt with CNNs for some years. Now, as of 2022, 
					CNNs are mostly used to deal with images.\\
					In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs \cite{wu2017introduction}. These networks use mostly three kind of layers: Dense layers (which are fully connected layers), 
					Convolutional layers and Pooling layers. In the following, there will be a short description of each kind of layer. 
					\begin{itemize}

@@

					Siamese neural networks, also called twin networks, are a more recent advance in computer science. These neural networks have a different structure from convolutional neural networks. The 
					structure of siamese neural networks is peculiar. In fact, there are two identical networks, called embedding networks, that process different inputs and, after that, 
					they merge in a single layer that measures the similarity between 
					the two outputs of the two networks. The siamese neural networks have a different application compared to CNNs, in fact twin networks are mainly used to measure similarity of two objects. 
					In the case of this paper, the siamese neural networks are used for image matching. This is not the first time that siamese networks are used for image matching, as shown in a paper written in 2016 by 
					Melekhov et al. \cite{melekhov2016siamese}, but with a little difference in the objective of the matching. The objective of the paper was to learn a general similarity for image retrieval, while on the case of this 
					paper, the objective is to find a similarity measure with a prototype.

@@

				\noindent In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017 \cite{appalaraju2017image}. In this work they explore the possibility to 
				find a similarity measure for image retrieval. To achieve this goal, they implemented a siamese neural network that uses two identical multi-scale CNNs that share weights. The ouput of the 
				network is binary, being $1$ the label to predict in case of negative examples and $0$ the label to predict in case of positive example. The loss function used in this work is a contrastive loss. This paper 
				then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspired by curriculum learning, that helps reducing the training time. \\
				This is not the only work that uses neural networks to learn similarity, in fact there are also other application fields for similarity study. One of them is healthcare, as shown in a paper by Suo et al., written in 
				2017, that introduces a model used to make personalized prediction of diseases for patients, basing the prediction on a similarity related method, learned using CNNs \cite{8217759}. In this paper, before 
				learning the actual similarity measure, the authors processed the input through a CNN and performed a step they call ``Time fusion''. This step let them incorporate the time information and 
				weight differently eventual symptoms based on their temporal distance from the first appearance of the disease. Only after this step the authors proceeded to learn a similarity metric, basing the learning 
				on CNNs.\\
				Another paper, written by Chopra et al. in 2005, used a method similar to the one written by Appalaraju. In this work, the authors used a siamese architecture to learn a similarity metric and applied it 
				in the field of face verification \cite{chopra2005learning}.\\
				More interestingly, there are also other papers, in particular a paper by Attarian et al. written in 2020 uses $VGG16$. This paper's goal is to use this CNN to predict human similarity 
				judgments \cite{attarian2020transforming}. Using $VGG16$, the authors were able to achieve good results, with over 90\% in validation accuracy.

@@

			\noindent Another possibility for collecting typicality values is the typicality ranking. With this method the researcher asks subjects to rank a set of objects based on their typicality. After doing so 
			and collecting the data, the researcher should infer the typicality values based on the ranking. The ranking, as the rating described in \ref{sec:typval}, cannot be performed on all images of the dataset, 
			so it is necessary to split the ranking and rank the images in different forms and then use the informations coming from different subjects and infer the informations about typicality from these answers.

@@

		\subsection{Considerations about the survey\label{sec:cas}}

			\subsubsection{Considerations}
				\noindent The first two presented methods have a quite similar concept behind them. Although it is still a matter of discussion which one is more reliable, especially in children, as seen in \cite{maridaki1997rating} 
				and \cite{10.1371/journal.pone.0157936}, both these methods have been used to collect typicality informations. The main difference in these two methods is that the first one, which is based on 
				ratings, the researchers may have biased data since it is possible that seeing a picture of an example of the category the subject can be biased. On the other hand, the other method does not present 
				this kind of bias, but presents a higher difficulty on in extracting the typicality values. \\
				The alternative possible proposed method, can show a lower bias than the bias of the rating method since no images influence the subject's ratings. Moreover, it is easier to infer a typicality value 
				than in the ranking method, since a higher position on the list corresponds to a higher typicality. 
				Another positive aspect of this method is that if a person did not think of a particular example, it will not appear on the ratings. This fact can help identifying the real typicality 
				without the possible bias introduced by presenting to a subject an image of an example that did not come to mind.

@@

				\noindent The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole 
				dataset, since it must have many images. In fact, it is very likely that a subject that has to rate or rank many examples will be tired after a certain number of images, polluting the results of the survey.
				The possible solution to this problem, is to give the subjects a subset of images to rate or rank. In this way, the collected data are most likely more reliable than the ones collected on all the dataset, 
				so it is more accurate the final result. \\
				Regarding only the typicality rating system, there is another problem. As hinted in previously, there is the possibility that this procedure leads to biased data. That is true because the form 
				created to collect the data, presents an example of an object that the subjects may not have thought of, and presenting the image, it may be possible that the subject gives a biased answer since 
				the image could have influenced the subject's judgement. For example, let us assume that the category chosen for the experiments is ``bird''. If a person is presented and image of a swan, 
				or a duck, and is asked to rate its typicality, most likely will rate it in the higher part of the scale, while if asked to list a certain number of birds it is more likely that it is not 
				present than that it is present.\\
				Talking about the ranking system, also this method can present biased data, since also this method presents the images, even if the bias is probably lower than the one that could result with the ranking system. 
				The major problem, with this method, is that the researcher must also design an algorithm to infer the typicality values from the rankings. This is a very difficult algorithm to design, since the rankings must 
				find a mapping to a scale.\\
				The alternative possibility described, can result in a lower bias since no images influence the subject's judgments. Recalling the previous example, in fact, if the subject did not think of 
				ducks and swans in the category ``bird'', these examples will not appear on the list. Although this technique presents a lower bias, it results in a great difficulty in prototype construction.
				\vspace{12pt}

@@

		\subsection{Considerations and difficulties on prototype construction\label{sec:cpc}}

			\noindent The prototype depends on the feature extraction technique that was used. As discussed in Section \ref{sec:fe}, the key difference is human interpretability. In fact, building a prototype using the 
			classical feature extraction methods, results in an image that can be seen and interpreted. Using a prototype generated with machine learning feature extraction techniques results in an array 
			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
			a work by Carvalho written in 2019 \cite{electronics8080832}, 
			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the European Union in the field of artificial intelligence. In particular, there is a document of 
			the act\footnote{\url{https://eur-lex.europa.eu/resource.html?uri=cellar:e0649735-a372-11eb-9585-01aa75ed71a1.0001.02/DOC_1&format=PDF}} that states that there will be some requirements in terms of 
			transparency and interpretability for machine learning systems that are considered high-risk AI. The growing interest produced some results, but still they are not enough to easily interpret machine learning 
			features. In particular, there are some interesting works regarding computer vision. Mahendran and Vedaldi, for example, explores image inversion techniques to understand to which extent it is possible to 
			reconstruct the image itself \cite{mahendran2015understanding}. In 2018, Lempitsky, Vedaldi and Ulyanov wrote a paper that shows how a randomly initialized network can be used to invert 
			deep neural representations \cite{8579082}.\\
			Most likely, especially considering the papers on image inversion,
			in the future will be possible to look at the features extracted by a neural network and comprehend their meaning. When this will be possible, independently of the feature extraction techniques 
			used, the human interpretability will be possible, and with that in mind it would be probably more convenient to extract the features using neural networks. The reason behind this consideration is 
			that although the training of a neural network can be expensive in computational terms, the evaluation of an input on a trained network it is not very computationally demanding. On the other side, algorithms 
			like the triangulation always have the same demand, that is lower than the demand of training a neural network, but surely higher than the demand of evaluating a single input on a convolutional neural network. 
			Moreover, considering the possibility to use transfer learning techniques, the training can become a fine-tuning or a domain adaptation problem, which means the computational load is lighter. Considering that 
			the fact that the training is a demanding task to be performed only once and that other algorithms may be less demanding but must be run multiple times, it is probably more convenient to train a neural 
			network. Moreover, not only the feature extraction process is convenient, but also the prototype construction itself is more convenient if the features are in the form of numerical parameters, since it is 
			enough to perform a weighted average, a simpler operation if confronted with the construction of a new image that should take into account features of numerous other images.
			Moreover, scientists will be presented a tough challenge, since the construction of an image using the average of other images is not an easy task. In this task there are in particular two problems. The first 
			one is that there is no clear algorithm to average two different images as it is requested in this paper, 
			and it is even more difficult to compute a weighted average. In fact, the in Figure \ref{fig:8}, it is difficult to even imagine what the result of this weighted average should be.

			\begin{figure*}[!t]
				\centering
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
				\end{subfigure}
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_2_edges.jpg}}
				\end{subfigure}
				\caption{Edge extraction of swifts in different poses}
				\label{fig:9}
			\end{figure*}
